In-Rank mesh optimization for URL customized promotion in SEO

### 2015-04-29 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag last version

  search engine optimization, e-commerce, page rank, in rank, mesh optimization, global optimization, tf/idf, Levenshtein, Hadoop, Spark GraphX, Neo4j

@@

  vector. We just end up with a vector with a smaller number of freedom degrees : our adjacency matrix is square but with large fixed null blocks resulting only from locations where links can't be added.

@@

  Notice that the prominence metrics vector we attribute mirrors the labels we gave. We hope to find back the natural arborescent structure from our algorithm.
  Let's now generate our initial population through sheer randomness. Let's visualize this population with this picture where x axe represents an individual chromosome, 
  while y axe runs over all the individuals of our population. We here don't categorize links, so you won't see large null streaks resulting from fixed null blocks in our adjacency matrix :

@@

  optimize. In that case, you would for instance rather optimize $\frac{1}{traffic\left(i\right)}$.

@@

@@

  One last remark here about a possible enhancement to our algorithm. As most e-commerce web sites tend to overlink web pages between themselves, 
  we could add a supplementary weigh to our optimization formula to rebalance link according to their semantic reliability.

@@

  \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} CS\left(i\right)\times f\left(X_i\right)\times PR(X_i)\right\}

@@

  where $CS(i)$ is a semantic distance between the two linked pages by $i$, for instance the cosinus of Salton. 

@@

  To be scalable is a must go for any e-commerce site which intends to grow !

>>>>

  search engine optimization, e-commerce, page rank, in rank, mesh optimization, global optimization, thematic page rank, tf/idf, Levenshtein, Hadoop, Spark GraphX, Neo4j

@@

  vector. We just end up with a vector with a smaller number of freedom degrees : our vectorized adjacency matrix has large fixed null blocks resulting from locations where links can't be added.

@@

  Notice that the prominence metrics vector we chose mirrors the labels we gave. We hope to find back the natural arborescent structure from our algorithm by giving appropriate values.
  The higher in the arborescence, the greater the value in the prominence vector. We end up with a bunch of small value for the product leaves. Let's now generate our initial population through sheer randomness. Let's visualize this population with this picture where x axe represents an individual chromosome, 
  while y axe runs over all the individuals of our population. We here don't have constraints on our links, so you won't see large null streaks resulting from fixed null blocks in our adjacency matrix :

@@

  optimize. In that case, you would for instance rather optimize $\left(\frac{1}{traffic\left(i\right)}\right)_{i \in \left\{1,...,N\right\}}$.

@@

  \section{Semantic in-rank}
  One last digression here is about a semantic enhancement to our algorithm. We have seen that we can force siloing navigation by enforcing constraints on our mesh.
  A natural way to enlarge this constraints not only to distinct universes but also between products within the same universe would be to use a semantic similarity metrics.
  As most e-commerce web sites tend to overlink web pages between themselves, this would allow us to enlighten and rebalance our links according to their semantic reliability.  
  We have here two ways to implement this. 

@@

  Either by incorporating our semantic coefficient directly in the computation of the page rank algorithm that computes $PR(X_i) \forall i$. 
  Or by enforcing the absence of links between two nodes when the semantic similarity between them is below a certain fixed similarity threshold t.

@@

  \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}\ G_{ij}=0 \ if \ CS(ij)\leq t}\left\{ \sum^{N}_{i=1} f\left(X_i\right)\times PR(X_i)\right\}

@@

  where $CS(ij)$ is a semantic distance between the two linked pages $i$ and $j$. $CS(ij)$ can be defined very easily as the scalar product of the tf/idf vectors of the
  product descriptions whose weight are defined by the well known formula :
  w_{ik}=\frac{tf_{ik}\log\left( \frac{N}{n_k}\right)}{\sqrt{\sum_{k=1}^t}(tf_{ik})^2 \log\left(\frac{N}{n_k}\right)^2}
  where $t$ is the number of terms in the production descripton, $tf_{ik}$ is the frequency of term $k$ in the product $i$ description, $n_{k}$ is the frequency of term $k$ in the corpus
  of all product descriptions and $N$ the total number of products. In an e-commerce world this formula might miss similarity between very specific product description 
  as they will appear as distinct terms in the tf/idf vector (for instance the battery DCI\_6020 vs DCI\_7020). That can be overcome by adding a Levenshtein distance to terms 
  with the highest inverse document corpus frequency between the two vectors.

@@

  To be scalable is a must for any e-commerce site which intends to grow !
